Test-driven Knowledge Graph Construction

### 2023-05-11 doc/paper4.tex
Mention XSLT unit tests
Mention release

We set to create a knowledge graph out of it to open it to a wider reuse and allow performing retrospective analyses of this data.
All artifacts we developed in this effort, such as CQs, are available as open source.\footnote{\url{https://github.com/KIZI/antigen-covid-tests-knowledge-graph}}

@@

\textbf{Step 6:} We started with implementing a transformation of the source data to RDF. We converted the input XML data into RDF/XML via an XSL transformation followed by SPARQL Update operations for post-processing. For example, we used post-processing for normalization of code-list values and manufacturers' names.

>>>>

We set to create a knowledge graph out of it to open it to a wider reuse and allow performing retrospective analyses of this data.
All artifacts we developed in this effort, such as CQs, are available as open source\footnote{\url{https://github.com/KIZI/antigen-covid-tests-knowledge-graph}} and the knowledge graph is released.\footnote{\url{https://github.com/KIZI/antigen-covid-tests-knowledge-graph/releases/tag/v1.0.0}}

@@

\textbf{Step 6:} We started with implementing a transformation of the source data to RDF. We converted the input XML data into RDF/XML via an XSL transformation followed by SPARQL Update operations for post-processing. For example, we used post-processing for normalization of code-list values and manufacturers' names. We also implemented few traditional unit tests of XSL functions within the transformation.
